---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# new.dist

<!-- badges: start -->
[![R-CMD-check](https://github.com/akmn35/new.dist/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/akmn35/new.dist/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The aim is to develop an R package,which is new.dist package, for the probability (density) function, the distribution function, the quantile function and the associated random number generation function for discrete and continuous distributions, which have recently been proposed in the literature. This package implements the following distributions: The Power Muth Distribution, A bimodal Weibull distribution, The discrete Lindley distribution, The gamma-Lomax distribution, weighted geometric distribution, A power log-Dagum distribution, kumaraswamy distribution, Lindley distribution, The unit-inverse Gaussian distribution, EP Distribution, Akash distribution, Ishita distribution, Maxwell distribution, The standard omega distribution, Slashed generalized Rayleigh distribution, Two-Parameter Rayleigh Distribution, On the Muth Distribution, Uniform-Geometric distribution, discrete Weibull distribution.

## Installation

You can install the development version of new.dist from [GitHub][https://github.com/] with:

``` r
# install.packages("devtools")
devtools::install_github("akmn35/new.dist")
```
## Details

```new.dist``` Density, distribution function, quantile function and random generation for parameter estimation of distributions.

## Example

```dbwd``` Density function for a Bimodal Weibull Distribution with parameters shape and scale.
```{r}
library(new.dist)
dbwd(1,alpha=2,beta=3,sigma=4)
```

```pbwd``` distribution function for a Bimodal Weibull Distribution with parameters shape and scale.
```{r}
library(new.dist)
pbwd(1,alpha=2,beta=3,sigma=4)

```

```qbwd``` quantile function for a Bimodal Weibull Distribution with parameters shape and scale.
```{r}
library(new.dist)
qbwd(.7,alpha=2,beta=3,sigma=4)
```

```rbwd``` random generation for a Bimodal Weibull Distribution with parameters shape and scale.
```{r}
library(new.dist)
  rbwd(5,alpha=2,beta=3,sigma=4)
```

```dsgrd``` Density function for a Slashed generalized Rayleigh distribution with parameters shape, scale and kurtosis.
```{r}
library(new.dist)
dsgrd(2,theta=3,alpha=1,q=4)
```

```psgrd``` Distribution function for a Slashed generalized Rayleigh distribution with parameters shape, scale and kurtosis.
```{r}
library(new.dist)
psgrd(5,theta=3,alpha=1,q=4)
```

```qsgrd``` quantile function for a Slashed generalized Rayleigh distribution with parameters shape, scale and kurtosis.
```{r}
library(new.dist)
qsgrd(.4,theta=3,alpha=1,q=4)
```

```rsgrd``` random generation for a Slashed generalized Rayleigh distribution with parameters shape, scale and kurtosis.
```{r}
library(new.dist)
  rsgrd(5,theta=3,alpha=1,q=4)
```

```dsod``` Density function for a the standard omega distribution with alpha and beta parameters.
```{r}
library(new.dist)
dsod(0.4, alpha=1, beta=2)
```

```psod``` Distribution function for a the standard omega distribution with alpha and beta parameters.
```{r}
library(new.dist)
psod(0.4, alpha=1, beta=2)
```

```qsod``` quantile function for a the standard omega distribution with alpha and beta parameters.
```{r}
library(new.dist)
qsod(.8, alpha=1, beta=2)
```

```rsod``` random generation for a the standard omega distribution with alpha and beta parameters.
```{r}
library(new.dist)
  rsod(5, alpha=1, beta=2)
```

```dugd``` Density function for the Uniform-Geometric distribution with theta parameters.
```{r}
library(new.dist)
dugd(1, theta=0.5)
```

```pugd``` Distribution function for the Uniform-Geometric distribution with theta parameters.
```{r}
library(new.dist)
pugd(1,theta=.5)
```

```qugd``` quantile function for the Uniform-Geometric distribution with theta parameters.
```{r}
library(new.dist)
qugd(0.6,theta=.1)
```

```rugd``` random generation for the Uniform-Geometric distribution with theta parameters.
```{r}
library(new.dist)
  rugd(5,theta=.1)
```

```dtpmd``` Density function for the Power Muth distribution with parameters shape and scale.
```{r}
library(new.dist)
dtpmd(1, beta=2, alpha=3)
```

```ptpmd``` Distribution function for the Power Muth distribution with parameters shape and scale.
```{r}
library(new.dist)
ptpmd(1,beta=2,alpha=3)
```

```qtpmd``` quantile function for the Power Muth distribution with parameters shape and scale.
```{r}
library(new.dist)
qtpmd(.5,beta=2,alpha=3)
```

```rtpmd``` random generation for the Power Muth distribution with parameters shape and scale.
```{r}
library(new.dist)
  rtpmd(5,beta=2,alpha=3)
```

```dtprd``` Density function for the Two-Parameter Rayleigh distribution with parameters location and scale.
```{r}
library(new.dist)
dtprd(5, lambda=4, mu=4)
```

```ptprd``` Distribution function for Two-Parameter Rayleigh distribution with parameters location and scale.
```{r}
library(new.dist)
ptprd(2,lambda=2,mu=1)
```

```qtprd``` quantile function for Two-Parameter Rayleigh distribution with parameters location and scale.
```{r}
library(new.dist)
qtprd(.5,lambda=2,mu=1)
```

```rtprd``` random generation for Two-Parameter Rayleigh distribution with parameters location and scale.
```{r}
library(new.dist)
  rtprd(5,lambda=2,mu=1)
```

```duigd``` Density function for the unit inverse Gaussian distribution with parameters mean and scale.
```{r}
library(new.dist)
duigd(1, mu=2, lambda=3)
```

```puigd``` Distribution function for the unit inverse Gaussian distribution with parameters mean and scale.
```{r}
library(new.dist)
puigd(1,mu=2,lambda=3)
```

```quigd``` quantile function for the unit inverse Gaussian distribution with parameters mean and scale.
```{r}
library(new.dist)
quigd(.1,mu=2,lambda=3)
```

```ruigd``` random generation for the unit inverse Gaussian distribution with parameters mean and scale.
```{r}
library(new.dist)
  ruigd(5,mu=2,lambda=3)
```

```dwgd``` Density function for the Weighted Geometric distribution with alpha and lambda parameters.
```{r}
library(new.dist)
dwgd(1,alpha=.2,lambda=3)
```

```pwgd``` Distribution function for the Weighted Geometric distribution with alpha and lambda parameters.
```{r}
library(new.dist)
dwgd(1,alpha=.2,lambda=3)
```

```qwgd``` quantile function for the Weighted Geometric distribution with alpha and lambda parameters.
```{r}
library(new.dist)
qwgd(.98,alpha=.2,lambda=3)
```

```rwgd``` random generation for the Weighted Geometric distribution with alpha and lambda parameters.
```{r}
library(new.dist)
  rwgd(5,alpha=.2,lambda=3)
```

```ddld``` Density function for the discrete Lindley distribution with theta parameters.
```{r}
library(new.dist)
ddld(1,theta=2)
```

```pdld``` Distribution function for the discrete Lindley distribution with theta parameters.
```{r}
library(new.dist)
ddld(1,theta=2)
```

```qdld``` quantile function for the discrete Lindley distribution with theta parameters.
```{r}
library(new.dist)
qdld(.993,theta=2)
```

```rdld``` random generation for the discrete Lindley distribution with theta parameters.
```{r}
library(new.dist)
  rdld(5,theta=1)
```

```demd``` Density function for a Maxwell distribution with theta parameters.
```{r}
library(new.dist)
demd(1,theta=2)
```

```pemd``` Distribution function for a Maxwell distribution with theta parameters.
```{r}
library(new.dist)
pemd(1,theta=2)
```

```qemd``` quantile function for a Maxwell distribution with theta parameters.
```{r}
library(new.dist)
qemd(.4,theta=5)
```

```remd``` random generation for a Maxwell distribution with theta parameters.
```{r}
library(new.dist)
  remd(5,theta=1)
```

```depkd``` Density function for kumaraswamy distribution with parameters shapes.
```{r}
library(new.dist)
depkd(0.1,lambda=2,alpha=3)
```

```pepkd``` Distribution function for kumaraswamy distribution with parameters shapes.
```{r}
library(new.dist)
depkd(0.1,lambda=2,alpha=3)
```

```qepkd``` quantile function for kumaraswamy distribution with parameters shapes.
```{r}
library(new.dist)
pepkd(0.5,lambda=2,alpha=3)
```

```repkd``` random generation for kumaraswamy distribution with parameters shapes.
```{r}
library(new.dist)
  repkd(5,lambda=2,alpha=3)
```

```dgld``` Density function for the gamma-Lomax Distribution with parameters shapes and beta parameter.
```{r}
library(new.dist)
dgld(1,a=2,alpha=3,beta=4)
```

```pgld``` distribution function for the gamma-Lomax Distribution with parameters shapes and beta parameter.
```{r}
library(new.dist)
dgld(1,a=2,alpha=3,beta=4)

```

```qgld``` quantile function for the gamma-Lomax Distribution with parameters shapes and beta parameter.
```{r}
library(new.dist)
qgld(.8,a=2,alpha=3,beta=4)
```

```rgld``` random generation for the gamma-Lomax Distribution with parameters shapes and beta parameter.
```{r}
library(new.dist)
  rgld(5,a=2,alpha=3,beta=4)
```

```dndd``` Density function for a new discrete distribution with parameters theta.
```{r}
library(new.dist)
dndd(2,theta=2)
```

```pndd``` Distribution function for a new discrete distribution with parameters theta.
```{r}
library(new.dist)
pndd(1,theta=2)
```

```qndd``` quantile function for a new discrete distribution with parameters theta.
```{r}
library(new.dist)
qndd(.5,theta=2)
```

```rndd``` random generation for a new discrete distribution with parameters theta.
```{r}
library(new.dist)
  rndd(5,theta=1)
```

```dnld``` Density function for the New Life distribution with lambda and beta parameters.
```{r}
library(new.dist)
dnld(1, lambda=2, beta=3)
```

```pnld``` Distribution function for the New Life distribution with lambda and beta parameters.
```{r}
library(new.dist)
pnld(1, lambda=2, beta=3)
```

```qnld``` quantile function for the New Life distribution with lambda and beta parameters.
```{r}
library(new.dist)
qnld(.8,lambda=2,beta=3)
```

```rnld``` random generation for the New Life distribution with lambda and beta parameters.
```{r}
library(new.dist)
  rnld(5,lambda=2,beta=3)
```

```dnoPDD``` Density function for a new one parameter discrete distribution with scale parameters.
```{r}
library(new.dist)
dnoPDD(1,theta=2)
```

```pnoPDD``` Distribution function for a new one parameter discrete distribution with scale parameters.
```{r}
library(new.dist)
pnoPDD(1,theta=2)
```

```qnoPDD``` quantile function for a new one parameter discrete distribution with scale parameters.
```{r}
library(new.dist)
dnoPDD(.8,theta=2)
```

```rnoPDD``` random generation for a new one parameter discrete distribution with scale parameters.
```{r}
library(new.dist)
  rnoPDD(5,theta=2)
```

```domd``` Density function for on the muth distribution with alpha parameters.
```{r}
library(new.dist)
domd(1,alpha=.2)
```

```pomd``` Distribution function for on the muth distribution with alpha parameters.
```{r}
library(new.dist)
pomd(1,alpha=.2)
```

```qomd``` quantile function for on the muth distribution with alpha parameters.
```{r}
library(new.dist)
qomd(.8,alpha=.2)
```

```romd``` random generation for on the muth distribution with alpha parameters.
```{r}
library(new.dist)
  domd(5,alpha=.2)
```

```dpldd``` Density function for a Power Log Dagum distribution with alpha, beta and theta parameters.
```{r}
library(new.dist)
dpldd(1, alpha=2, beta=3, theta=4)
```

```ppldd``` Distribution function for a Power Log Dagum distribution with alpha, beta and theta parameters.
```{r}
library(new.dist)
ppldd(1, alpha=2, beta=3, theta=4)
```

```qpldd``` quantile function for a Power Log Dagum distribution with alpha, beta and theta parameters.
```{r}
library(new.dist)
qpldd(.8, alpha=2, beta=3, theta=4)
```

```rpldd``` random generation for a Power Log Dagum distribution with alpha, beta and theta parameters.
```{r}
library(new.dist)
  rpldd(5, alpha=2, beta=3, theta=4)
```

```drld``` Density function for a  lindley distribution with parameters theta.
```{r}
library(new.dist)
drld(1,theta=2)
```

```prld``` Distribution function for a  lindley distribution with parameters theta.
```{r}
library(new.dist)
prld(1,theta=2)
```

```qrld``` quantile function for a  lindley distribution with parameters theta.
```{r}
library(new.dist)
qrld(.5,theta=2)
```

```rrld``` random generation for a lindley distribution with parameters theta.
```{r}
library(new.dist)
  rrld(5,theta=1)
```

## Corresponding Author
Department of Statistics, Faculty of Science, Selcuk University, 42250, Konya, Turkey  <br />
Email:coskun@selcuk.edu.tr

## References 
Vila, R. ve Niyazi Çankaya, M., 2022,
*A bimodal Weibull distribution: properties and inference*,Journal of Applied Statistics, 49 (12), 3044-3062.

Iriarte, Y. A., Vilca, F., Varela, H. ve Gómez, H. W., 2017,
*Slashed generalized Rayleigh distribution*, Communications in Statistics-Theory and Methods, 46 (10), 4686-4699.

Birbiçer, İ. ve Genç, A. İ., 2022,
*On parameter estimation of the standard omega distribution*. Journal of Applied Statistics, 1-17.

Akdoğan, Y., Kuş, C., Asgharzadeh, A., Kınacı, İ., & Sharafi, F. (2016).
*Uniform-geometric distribution*. Journal of Statistical Computation and Simulation, 86(9), 1754-1770.

Jodra, P., Gomez, H. W., Jimenez-Gamero, M. D., & Alba-Fernandez, M. V. (2017).
*The power Muth distribution* . Mathematical Modelling and Analysis, 22(2), 186-201.

Dey, S., Dey, T. ve Kundu, D., 2014,
*Two-parameter Rayleigh distribution: different methods of estimation*, American Journal of Mathematical and Management Sciences, 33 (1), 55-74.

Ghitany, M., Mazucheli, J., Menezes, A. ve Alqallaf, F., 2019,
*The unit-inverse Gaussian distribution: A new alternative to two-parameter distributions on the unit interval*, Communications in Statistics-Theory and Methods, 48 (14), 3423-3438.

Najarzadegan, H., Alamatsaz, M. H., Kazemi, I. ve Kundu, D., 2020,
*Weighted bivariate geometric distribution: Simulation and estimation*, Communications in Statistics-Simulation and Computation, 49 (9), 2419-2443.

Gómez-Déniz, E. ve Calderín-Ojeda, E., 2011,
*The discrete Lindley distribution: properties and applications*.Journal of statistical computation and simulation, 81 (11), 1405-1416.

Krishna, H., Vivekanand ve Kumar, K., 2015,
*Estimation in Maxwell distribution with randomly censored data*, Journal of statistical computation and simulation, 85 (17), 3560-3578.

Kohansal, A. ve Bakouch, H. S., 2021,
*Estimation procedures for Kumaraswamy distribution parameters under adaptive type-II hybrid progressive censoring*, Communications in Statistics-Simulation and Computation, 50 (12), 4059-4078.

Cordeiro, G. M., Ortega, E. M. ve Popović, B. V., 2015,
*The gamma-Lomax distribution*, Journal of statistical computation and simulation, 85 (2), 305-319.

Bakouch, H. S., Jazi, M. A. ve Nadarajah, S., 2014,
*A new discrete distribution, Statistics*, 48 (1), 200-240.

Kuş, C., 2007,
*A new lifetime distribution*, Computational Statistics & Data Analysis, 51 (9), 4497-4509.

Shukla, K. K., Shanker, R. ve Tiwari, M. K., 2022,
*A new one parameter discrete distribution and its applications*, Journal of Statistics and Management Systems, 25 (1), 269-283.

Jodrá, P., Jiménez-Gamero, M. D. ve Alba-Fernández, M. V., 2015,
*On the Muth distribution, Mathematical Modelling and Analysis*, 20 (3), 291-310.

Bakouch, H. S., Khan, M. N., Hussain, T. ve Chesneau, C., 2019,
*A power log-Dagum distribution: estimation and applications*, Journal of Applied Statistics, 46 (5), 874-892.

Akgül, F. G., Acıtaş, Ş. ve Şenoğlu, B., 2018,
*Inferences on stress–strength reliability based on ranked set sampling data in case of Lindley distribution*, Journal of statistical computation and simulation, 88 (15), 3018-3032.
